Exploring probability distributions for bivariate temporal granularities

### 2019-12-14 main.Rmd
changing section visualization

Creating a visualisation requires a number of nuanced judgements. We exploit some features of layers and faceting [@Wilkinson1999-nk] and [@Wickham2009-pk] to come up with a recommendation system while visualizing the distribution of the "dependent" variable across bivariate cyclic temporal granularities with the data structure <$A_i$, $B_j(s)$, $v(s)$> $i \in {1, 2, \dots, n}$ and $j \in {1, 2, \dots, m}$. The framework involves faceting approach with one cyclic granularity plotted along the x-axis, the other one across facet and the dependent time series variable on the y-axis. Different distribution plots might be appropriate depending on which features of the distrbution we are interested to look at, the levels of time granularities being plotted, how granularities interact and number of observations available. We will look at each of these aspects separately and analyze the effect of each on visualization.

>>>>

The three key components of every visualization is: data, aesthetic mappings between variables in the data and visual attributes, and at least one layer which describes how to render each observation. Layers are usually created with a geom function. Considering the data structure <$A_i$, $B_j(s)$, $v(s)$> $i \in {1, 2, \dots, n}$ and $j \in {1, 2, \dots, m}$, visualizations can be defined by:
- Data: <$A_i$, $B_j(s)$, $v(s)$> $i \in {1, 2, \dots, n}$
- Aesthetic mapping: $A_i$ mapped to $x$ position and $v(s)$ to $y$ position.
- Layer: any geom that summarizes distribution

To add additional variables to a plot, we can use other aesthetics like colour, shape, and size or facetting. Facetting creates tables of graphics by displaying the same graph for each subset.
- Facet:  $B_j(s)$

We exploit some features of layers and faceting [@Wilkinson1999-nk] and [@Wickham2009-pk] to come up with a recommendation system while visualizing the distribution of the "dependent" variable across bivariate cyclic temporal granularities with the data structure <$A_i$, $B_j(s)$, $v(s)$> $i \in {1, 2, \dots, n}$ and $j \in {1, 2, \dots, m}$. The framework involves faceting approach with one cyclic granularity plotted along the x-axis, the other one across facet and the dependent time series variable on the y-axis. Different distribution plots might be appropriate depending on which features of the distrbution we are interested to look at, the levels of time granularities being plotted, how granularities interact and number of observations available. We will look at each of these aspects separately and analyze the effect of each on visualization.
